Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2024-05-06 paper/paper.tex
feat(paper): Add section about codeocean and wandb

>>>>

There are commercial, domain specifig solutions, e.g. CodeOcean\footnote{\url{https://codeocean.com/}} for bioinformatics or Weights and Biases\footnote{\url{https://wandb.ai/site}} for machine learning.
With these archiving platforms, experiments can be run using technologies like docker so they can be verified by other scientists.
Those commercial platforms are closed source, so the source code cannot be reviewed nor adjusted as also discussed by~\cite{koch2023sustainable}.
